% LaTeX resume using res.cls
%\documentclass[line,margin]{res} 
\documentclass[line]{res}
\usepackage{pifont}
\usepackage{amssymb}
\usepackage{graphics}
%\usepackage{url}
\usepackage[hidelinks]{hyperref}
\usepackage{fontawesome}
\usepackage{libertine}
\usepackage{enumitem}
%\usepackage[scaled]{beramono}
%\usepackage[urw-garamond]{mathdesign}
%
\renewcommand{\familydefault}{\sfdefault}
\renewcommand{\ttdefault}{lmtt}
\renewcommand{\labelitemi}{\scalebox{0.8}{\ding{70}}}
\renewcommand{\labelitemii}{\raisebox{0.12em}{\scalebox{0.6}{\ding{71}}}}
\setlist[itemize]{itemsep=1pt, parsep=0pt}
%	\addtolength{\oddsidemargin}{-.4in}
%	\addtolength{\evensidemargin}{-.4in}
%  	\addtolength{\textwidth}{0.8in}
\begin{document}

\name{\Huge{Joel Mackenzie}}
% \address used twice to have two lines of address
\address{\faMapMarker~\greytext{Brisbane, Queensland, Australia}}
% JMM: REST OF HEADER LINES ARE IN STYLE FILE DUE TO SHITTY LATEX CODE

\begin{resume}

\section{Education}{\bf Doctorate of Philosophy (Computer Science).}\hfill \greytext{February 2016 -- October 2019}\\
                    PhD Thesis: {\emph{Managing Tail Latency in Large Scale Information Retrieval Systems.}}\\
                    RMIT University, Melbourne, Australia.\\\\
                    {\bf Bachelor of Computer Science, Hons (First Class).}\hfill \greytext{February 2012 -- November 2015}\\
                    Honours Thesis: {\emph{Efficiency-Effectiveness Trade-offs for Location Aware Search.}}\\
                    RMIT University, Melbourne, Australia.
               

\section{Work Experience}
                    {\bf The University of Queensland} -- Lecturer\hfill \greytext{February 2021 -- Present}\\
                    Teaching and Research in Computer Science, focusing on Information Retrieval and Data Science.

                    {\bf The University of Melbourne} -- Postdoctoral Research Fellow\hfill \greytext{February 2020 -- January 2021}\\
                    Worked with Prof. Alistair Moffat on the ARC Discovery Project {\emph{Efficient Compression and Querying Techniques for Massive Text Collections.}}

                    {\bf RMIT University} -- Research Assistant\hfill \greytext{October 2019 -- February 2020}\\
                    Worked with Prof. Shane Culpepper on a number of Information Retrieval research projects.

                    {\bf Microsoft Research} -- Research Intern\hfill \greytext{June 2018 -- September 2018}\\
                    Worked with the SQI and the Language and Information Technologies teams to understand user behavior in the email search domain. Involved analysis of user behavior logs from a set of human intelligence tasks related to email search.
 
                    %{\bf RMIT University} -- Programmer\hfill \greytext{May 2017 -- September 2017}\\
                    %Data preparation and scripting for the RMIT Computing department for the Australian Research Council's ``Excellence in Research for Australia'' rankings. Involved writing tools to automatically extract and analyze citation information from both Google Scholar and Microsoft Academic.

                    {\bf Envato} -- Assistant Search Engine Analyst (Intern)\hfill \greytext{January 2016 -- April 2016}\\
                    Worked with the Discovery team to continue improving search effectiveness across some of Envato's most popular marketplaces. Involved creating tooling for analysis of query logs to gain insights into the search behaviour
of users on Envato market.

%\section{Teaching Experience} 
%                     {\bf RMIT University} -- Head Tutor/Tutor/Lab assistant\hfill \greytext{July 2014 -- Present}\\
%                      Tutored and assisted in labs for the Operating Systems, Database Systems, Computing Theory and Information Retrieval courses. Head tutor for the Programming Fundamentals course.
%This involved preparation and delivery of both theoretical and practical knowledge and tasks to students, ranging from programming
%and algorithms to mathematics and statistics.
%
\section{Teaching Experience}
                     {\bf The University of Queensland}\hfill
                      \begin{itemize}[topsep=3pt]
                        \item Algorithms \& Data Structures -- Course coordinator and Lecturer. \hfill \greytext{Semester 2, 2023.}
                        \item Introduction to Data Science -- Course coordinator and Lecturer. \hfill \greytext{Semester 1, 2023.}
                        \item Advanced Database Systems -- Course coordinator and Lecturer. \hfill \greytext{Semester 2, 2022.}
                      \end{itemize}
                     {\bf RMIT University}\hfill %\greytext{July 2014 -- July 2019}
                      \begin{itemize}[topsep=3pt]
                        %\item I have been a head tutor, tutor, and lab assistant for courses such as {\emph{Database Systems,
                        %  Information Retrieval, Programming Fundamentals, Computing Theory,}} and {\emph{Operating Systems
                        %  Principles}}.
                        \item Database Systems -- Tutor and lab assistant. \hfill \greytext{Semester 1, 2015, and Semester 1, 2019.}
                          %\begin{itemize}
                          %  \item \greytext{Semester 1, 2015 and Semester 1, 2019.}
                          %\end{itemize} 
                        \item Information Retrieval -- Tutor. \hfill \greytext{Semester 1, 2017, and Semester 1, 2018.}
                          %\begin{itemize}
                         %   \item \greytext{Semester 1, 2017 and Semester 1, 2018.}
                         % \end{itemize}
                        \item Programming Fundamentals -- Head tutor. \hfill \greytext{Semester 1, 2018.}
                          %\begin{itemize}
                          %  \item \greytext{Semester 1, 2018.}
                          %\end{itemize}
                        \item Computing Theory -- Tutor. \hfill \greytext{Semester 1, 2015.}
                          %\begin{itemize}
                         %    \item \greytext{Semester 1, 2015.}
                         % \end{itemize} 
                        \item Operating Systems Principles -- Tutor and lab assistant. \hfill \greytext{Semester 2, 2014.}
                         % \begin{itemize}
                         %   \item \greytext{Semester 2, 2014.}
                         % \end{itemize}
                     \end{itemize}
%This involved preparation and delivery of both theoretical and practical knowledge and tasks to students, ranging from programming
%and algorithms to mathematics and statistics.
%\clearpage
\section{Research Interests}{
I am primarily interested in the discipline of Information Retrieval, including efficient indexing
and retrieval, ranking, evaluation, and user behavior. I also have an interest in data structures and
algorithms.
}
 
\section{Publications} 
                       J. Mackenzie and A. Moffat: \pubtext{Index-Based Batch Query Processing Revisited.}
                       In {\it\greytext{Proceedings of the 45th European Conference on Information Retrieval (ECIR 2023)}},
                       April, 2023. Long paper (reproducibility track).\\[1.5ex]
                       A. Moffat and J. Mackenzie: \pubtext{Efficient Immediate-Access Dynamic Indexing.}
                       In {\it\greytext{Information Processing and Management (IPM)}}, 2023, Journal Paper.\\[1.5ex]
                       J. Mackenzie and A. Trotman and J. Lin: \pubtext{Efficient Document-at-a-Time and Score-at-a-Time Query Evaluation for Learned Sparse Representations.}
                       In {\it{ACM Transactions on Information Systems (TOIS)}}, 2022, Journal Paper.\\[1.5ex]
                       A. Moffat and J. Mackenzie: \pubtext{Immediate-Access Indexing Using Space-Efficient Extensible Arrays.}
                       In {\it{Proceedings of the 26th Australasian Document Computing Symposium (ADCS 2022)}}, December, 2022.\\[1.5ex]
                       J. Mackenzie, A. Mallia, A. Moffat, and M. Petri: \pubtext{Accelerating Learned Sparse Indexes Via Term Impact Decomposition.}
                       In {\it{\greytext{Findings of the Association for Computational Linguistics: EMNLP 2022 (EMNLP Findings 2022)}}}, December, 2022. Full paper.\\[1.5ex]
                       J. Mackenzie, M. Petri, and A. Moffat: \pubtext{Tradeoff Options for Bipartite Graph Partitioning.}
                       In {\it\greytext{IEEE Transactions on Data Engineering (TKDE)}}, 2022. Journal paper.\\[1.5ex]
                       J. Mackenzie, M. Petri, and L. Gallagher: \pubtext{IOQP: A simple Impact-Ordered Query Processor written in Rust.}
                       In {\it\greytext{Proceedings of the 3rd International Conference on Design of Experimental Search and Information Retrieval Systems (DESIRES 2022)}}, August, 2022. Full paper.\\[1.5ex]
                       D. La Barbera, K. Roitero, J. Mackenzie, D. Spina, G. Demartini, and S. Mizzaro: \pubtext{Brisbane--Udine--Melbourne at CLEF2022 CheckThat! Lab: A Composite Deep Learning Approach to Fake News Detection using Evidence Retrieval.}
                       In {\it\greytext{Working Notes of CLEF 2022 - Conference and Labs of the Evaluation Forum (CLEF 2022)}}, September, 2022. Notebook paper.\\[1.5ex]
                       A. Moffat, J. Mackenzie, P. Thomas, and L. Azzopardi: \pubtext{A Flexible Framework for Offline Effectiveness Metrics.}
                       In {\it\greytext{Proceedings of the 45th International ACM Conference on Research and Development in Information Retrieval (SIGIR 2022)}}, July, 2022. Long paper.\\[1.5ex]
                       A. Mallia, J. Mackenzie, T. Suel, and N. Tonellotto: \pubtext{Faster Learned Sparse Retrieval with Guided Traversal.}
                       In {\it\greytext{Proceedings of the 45th International ACM Conference on Research and Development in Information Retrieval (SIGIR 2022)}}, July, 2022. Short paper.\\[1.5ex]
                       A. Trotman, J. Mackenzie, P. Parameswaran, and J. Lin: \pubtext{A Common Framework for Exploring Document-at-a-Time and Score-at-a-Time Retrieval Methods.}
                       In {\it\greytext{Proceedings of the 45th International ACM Conference on Research and Development in Information Retrieval (SIGIR 2022)}}, July, 2022. Demo paper.\\[1.5ex]
                       J. Mackenzie and D. Spina: \pubtext{Report on the 25th Australasian Document Computing Symposium (ADCS 2021).}
                       In {\it\greytext{SIGIR Forum}}, 2022. Event report.\\[1.5ex]
                       J. Mackenzie, M. Petri, and A. Moffat: \pubtext{Efficient Query Processing Techniques for Next-Page Retrieval.}
                       In {\it\greytext{Information Retrieval Journal (IRJ)}}, 2022. Journal paper.\\[1.5ex]
                       J. Mackenzie, M. Petri, and A. Moffat: \pubtext{Anytime Ranking on Document-Ordered Indexes.}
                       In {\it\greytext{ACM Transactions on Information Systems (TOIS)}}, 2022. Journal paper.\\[1.5ex]
                       A. Moffat and J. Mackenzie: \pubtext{Conferences, Journals, Preprints, and Reviewer Expectations.}
                       In {\it\greytext{SIGIR Forum}}, 2021. Opinion paper.\\[1.5ex]
                       J. Mackenzie and A. Moffat: \pubtext{Cost-Effective Updating of Distributed Reordered Indexes.}
                       In {\it\greytext{Proceedings of the 25th Australasian Document Computing Symposium (ADCS 2021)}}, December, 2021. \explainc{Best paper award.}\\[1.5ex]
                       J. Mackenzie, M. Petri, and A. Moffat: \pubtext{A Sensitivity Analysis of the MSMARCO Collection.}
                       Unpublished technical report, 2021. Available: {\url{https://arxiv.org/abs/2112.03396}}.\\[1.5ex]
                       J. Lin, X. Ma, J. Mackenzie, and A. Mallia: \pubtext{On the Separation of Logical and Physical Ranking Models for Text Retrieval Applications.}
                       In {\it\greytext{Proceedings of the Second Biennial Conference on Design of Experimental Search and Information Retrieval Systems (DESIRES 2021)}}, September, 2021. Short paper.\\[1.5ex]
                       J. Mackenzie, M. Petri, and A. Moffat: \pubtext{Faster Index Reordering with Bipartite Graph Partitioning.}
                       In {\it\greytext{Proceedings of the 44th International ACM Conference on Research and Development in Information Retrieval (SIGIR 2021)}}, July, 2021. Short paper.\\[1.5ex]
                       L. Azzopardi, J. Mackenzie, and A. Moffat: \pubtext{ERR is not C/W/L: Exploring the Relationship Between Expected Reciprocal Rank and Other Metrics.}
                       In {\it\greytext{Proceedings of the 2021 ACM SIGIR International Conference on the Theory of Information Retrieval (ICTIR 2021)}}, July, 2021. \explainc{Best paper award.}\\[1.5ex]
                       J. Mackenzie and A. Moffat: \pubtext{Modality Effects When Simulating User Querying Tasks.}
                       In {\it\greytext{Proceedings of the 2021 ACM SIGIR International Conference on the Theory of Information Retrieval (ICTIR 2021)}}, July, 2021.\\[1.5ex]
                       R. Benham, J. Mackenzie, J. S. Culpepper, and A. Moffat: \pubtext{Different Keystrokes for Different Folks: Visualizing Crowdworker Querying Behavior.}
                       In {\it\greytext{Proceedings of the 6th ACM SIGIR Conference on Human Information Interaction and Retrieval (CHIIR 2021)}}, March, 2021. Demo paper.\\[1.5ex]
                       J. Mackenzie and A. Moffat: \pubtext{Examining the Additivity of Top-$k$ Query Processing Innovations.}
                       In {\it\greytext{Proceedings of the 29th ACM International Conference on Information and Knowledge Management (CIKM 2020)}}, October, 2020. Long paper.\\[1.5ex]
                       J. Mackenzie, R. Benham, M. Petri, J. R. Trippas, J. S. Culpepper, and A. Moffat: \pubtext{CC-News-En: A Large English News Corpus}
                       In {\it\greytext{Proceedings of the 29th ACM International Conference on Information and Knowledge Management (CIKM 2020)}}, October, 2020. Resource paper.\\[1.5ex]
                       J. Mackenzie, Z. Dai, L. Gallagher, and J. Callan: \pubtext{Efficiency Implications of Term Weighting for Passage Retrieval.}
                       In {\it\greytext{Proceedings of the 43rd International ACM Conference on Research and Development in Information Retrieval (SIGIR 2020)}}, July, 2020. Short paper.\\[1.5ex]
                       J. Lin, J. Mackenzie, C. Kamphuis, C. Macdonald, A. Mallia, M. Siedlaczek, A. Trotman, and A. de Vries: \pubtext{Supporting Interoperability Between Open-Source Search Engines with the Common Index File Format.}
                       In {\it\greytext{Proceedings of the 43rd International ACM Conference on Research and Development in Information Retrieval (SIGIR 2020)}}, July, 2020. Demo paper.\\[1.5ex]
                       R. Benham, J. Mackenzie, A. Moffat, and J. S. Culpepper: \pubtext{Boosting Search Performance Using Query Variations.} 
                       In {\it\greytext{ACM Transactions on Information Systems (TOIS)}}, October, 2019. Journal paper.\\[1.5ex] 
                       A. Mallia, M. Siedlaczek, J. Mackenzie, and T. Suel: \pubtext{PISA: Performant Indexes and Search for Academia.}
                       In {\it\greytext{Proceedings of the Open-Source IR Replicability Challenge, co-located with SIGIR (OSIRRC 2019)}},
                       July, 2019. Workshop paper.\\[1.5ex]
                       M. Petri, A. Moffat, J. Mackenzie, J. S. Culpepper, and D. Beck: \pubtext{Accelerated Query Processing Via Similarity Score Prediction.}
                       In {\it\greytext{Proceedings of the 42nd International ACM Conference on Research and Development in Information Retrieval (SIGIR 2019)}},
                       July, 2019. Long paper.\\[1.5ex]
                       J. Mackenzie, K. Gupta, F. Qiao, A. H. Awadallah, and M. Shokouhi: \pubtext{Exploring User Behavior in Email Re-Finding Tasks.}
                       In {\it\greytext{Proceedings of the 2019 World Wide Web Conference (WWW 2019)}},
                       May, 2019. Long paper.\\[1.5ex] 
                       J. Mackenzie, A. Mallia, M. Petri, J. S. Culpepper, and T. Suel: \pubtext{Compressing Inverted Indexes with Recursive Graph Bisection: A Reproducibility Study.}
                       In {\it\greytext{Proceedings of the 41st European Conference on Information Retrieval (ECIR 2019)}},
                       April, 2019. Long paper (reproducibility track).\\[1.5ex]
                       L. Gallagher, J. Mackenzie, and J. S. Culpepper: \pubtext{Revisiting Spam Filtering in Web Search.}
                       In {\it\greytext{Proceedings of the 23rd Annual Australasian Document Computing Symposium (ADCS 2018)}},
                       December, 2018. Short paper.\\[1.5ex]
                       R. Benham, L. Gallagher, J. Mackenzie, B. Liu, X. Lu, F. Scholer, A. Moffat, and J. S. Culpepper: \pubtext{RMIT at the 2018 TREC CORE Track.}
                       In {\it\greytext{Proceedings of the 27th Text REtrieval Conference (TREC 2018)}},
                       November, 2018. Notebook paper.\\[1.5ex]
                       R. Benham, J. S. Culpepper, L. Gallagher, X. Lu, and J. Mackenzie : \pubtext{Towards Efficient and Effective Query Variant Generation.}
                       In {\it\greytext{Proceedings of the First Biennial Conference on Design of Experimental Search and Information Retrieval Systems (DESIRES 2018)}},
                       August, 2018. Long paper.\\[1.5ex]
                       J. Mackenzie, C. Macdonald, F. Scholer, and J. S. Culpepper: \pubtext{On the Cost of Negation for Dynamic Pruning.}
                       In {\it\greytext{Proceedings of the 40th European Conference on Information Retrieval (ECIR 2018)}},
                       March, 2018. Short paper.\\[1.5ex]
                       J. Mackenzie, J. S. Culpepper, R. Blanco, M. Crane, C. L. A. Clarke, and J. Lin: \pubtext{Query Driven Algorithm Selection in Early Stage Retrieval.}
                       In {\it\greytext{Proceedings of the 11th International ACM Conference on Web Search and Data Mining (WSDM 2018)}},
                       February, 2018. Long paper.\\[1.5ex]
                       J. Mackenzie, F. Scholer, and J. S. Culpepper: \pubtext{Early Termination Heuristics for Score-at-a-Time Index Traversal.}
                       In {\it\greytext{Proceedings of the 22nd Annual Australasian Document Computing Symposium (ADCS 2017)}},
                       December, 2017. Long paper. \explainc{Runner up best paper award.}\\[1.5ex]
                       L. Gallagher, J. Mackenzie, R. Benham, R-C. Chen, F. Scholer, and J. S. Culpepper: \pubtext{RMIT at the NTCIR-13 We Want Web Task.}
                       In {\it\greytext{Proceedings of the 13th NTCIR Conference on Evaluation of Information Access Technologies (NTCIR 2017)}},
                       December, 2017. Notebook paper.\\[1.5ex]
                       R. Benham, L. Gallagher, J. Mackenzie, T. T. Damessie, R-C. Chen, F. Scholer, A. Moffat, and J. S. Culpepper: \pubtext{RMIT at the 2017 TREC CORE Track.}
                       In {\it\greytext{Proceedings of the 26th Text REtrieval Conference (TREC 2017)}},
                       November, 2017. Notebook paper.\\[1.5ex]
                       J. Mackenzie: \pubtext{Managing Tail Latencies in Large Scale IR Systems.}
                       In {\it\greytext{Proceedings of the 40th International ACM Conference on Research and Development in Information Retrieval (SIGIR 2017)}},
                       August, 2017. Extended abstract.\\[1.5ex]
                       M. Crane, J. S. Culpepper, J. Lin, J. Mackenzie, and A. Trotman: \pubtext{A Comparison of Document-at-a-Time and Score-at-a-Time Query Evaluation.}
                       In {\it\greytext{Proceedings of the 10th International ACM Conference on Web Search and Data Mining (WSDM 2017)}},
                       February, 2017. Long paper.\\[1.5ex]
                       J. Mackenzie, R-C. Chen, and J. S. Culpepper: \pubtext{RMIT at TREC 2016 LiveQA Track.}
                       In {\it\greytext{Proceedings of the 25th Text REtrieval Conference (TREC 2016)}},
                       November, 2016. Notebook paper.\\[1.5ex]
                       J. Mackenzie, F. M. Choudhury, and J. S. Culpepper: \pubtext{Efficient Location-Aware Web Search.}
                       In {\it\greytext{Proceedings of the 20th Annual Australasian Document Computing Symposium (ADCS 2015)}},
                       December, 2015. Long paper. \explainc{Best paper award.}

\section{Publicity}
{\bf{Amazon Science Blog:}} Article titled {\emph{``More efficient and reliable retrieval of distributed data''}}
features our 2021 ACM TOIS publication {\emph{``Anytime Ranking on Document-Ordered Indexes.''}}

\section{Awards and Funding}
  {\bf The University of Queensland New Staff Research Grant (2022):} \$50,000.\\
  {\bf The University of Melbourne Early Career Seed Funding (2021):} \$20,000.\\
  {\bf Best Paper Award:} ADCS 2021, ICTIR 2021, ADCS 2017 (Runner up), ADCS 2015.\\
  {\bf RMIT CIDDA CReD Research Excellence Award:} For {\emph{``Exploring User Behavior in Email Re-Finding Tasks''}} (WWW 2019).\\
  {\bf RMIT TIGER/BDDA Group Student Paper Award:} For {\emph{``Query Driven Algorithm Selection in Early Stage Retrieval''}} (WSDM 2018).\\
  {\bf SIGIR Travel Award:}  SIGIR 2017, WSDM 2017.\\
  {\bf Australian Postgraduate Award:} PhD scholarship from 2016 to 2019.\\
  {\bf RMIT Vice Chancellors List Award} (Top $2\%$ of higher education university-wide): 2014, 2015.

\section{Service}
{\bf General Chair}\\
  Australasian Document Computing Symposium (ADCS) 2021.\\[1.2ex]
{\bf Program Chair}\\
  Australasian Document Computing Symposium (ADCS) 2022.\\[1.2ex]
{\bf Proceedings Chair}\\
      ACM SIGIR Conference on Human Information Interaction and Retrieval (CHIIR) 2021.\\
      International ACM Conference on Web Search and Data Mining (WSDM) 2019.\\[1.2ex]
{\bf{SIGIR Artifact Evaluation Committee (AEC)}}\\
Member: 2021--Present.\\[1.2ex]
{\bf{Area Chair}}\\
International Conference on Computational Linguistics (COLING) 2022.\\[1.2ex]
{\bf Program Committee Member or Reviewer}\\
Australasian Document Computing Symposium (ADCS): 2016--2019.\\
International ACM Conference on Information and Knowledge Management (CIKM): 2016--2022.\\
European Conference on Information Retrieval (ECIR): 2021--2023.\\
Empirical Methods in Natural Language Processing (EMNLP): 2020--2022.\\
The Journal of Information Science: 2019.\\
ACM SIGKDD International Conference on Knowledge Discovery and Data Mining (KDD): 2021.\\
International ACM Conference on Research and Development in Information Retrieval (SIGIR): 2019--2022.\\
International Symposium on String Processing and Information Retrieval (SPIRE): 2019.\\
IEEE Transactions on Knowledge and Data Engineering (TKDE): 2022.\\
ACM Transaction on Information Systems (TOIS): 2020. \\ 
The International Journal on Very Large Databases (VLDB): 2017.\\
Workshop on Insights from Negative Results in NLP: 2022 (at ACL).\\
International ACM Conference on Web Search and Data Mining (WSDM): 2021--2023.\\
The World Wide Web Conference (TheWebConf, {\emph{aka}} WWW): 2022--2023.\\[1.2ex]
I also review grants for the Australian Research Council.

%
%\section{Skills}{\bf Programming Languages:} Awk, Bash, C, C++, Java, Javascript, PHP, Python, and R.\\[1.5ex]
%                {\bf Databases systems:} MongoDB, MySQL, and Redis.\\[1.5ex]
%                {\bf Operating Systems:} Linux (Debian and derivatives preferred), Unix (Solaris), Windows, and OS X.\\[1.5ex]
%                {\bf Tools and Environment:} GNU Toolchain, Valgrind, Eclipse, Vim, Git, and \LaTeX.\\[1.5ex]
%                {\bf Search Engine Tools:} PISA, Indri, and Terrier.\\[1.5ex]
%                {\bf Learning frameworks:} QuickRank, JForests, LightGBM, and Weka.
%

%\section{References}
%  References and academic transcripts can be provided upon request.
\end{resume}
\end{document}
